### 2024-11-14 Article/Graph_sections/Eq_Graphs_integration.tex
proof of 2.2.12

Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$ and $h = (h_E, h_V, h_C)$ to $h_C$.

@@

{\color{red}
\begin{prop}\label{prop:quot_creat_colims}
    $Q$ creates colimits.
\end{prop}
}

\begin{proof}
    Preserve from \Cref{th:adjoints_preserves_lim}. Remain to see Reflect.
\end{proof}

>>>>

Another functor that will be useful later is $V: \EqGrph \to \Set$, that sends $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.

@@

{\color{red}
\begin{prop}\label{prop:quot_creat_colims}
    $Q$ creates colimits.
\end{prop}

\begin{proof}
    Preserve from \Cref{th:adjoints_preserves_lim}. Remain to see Reflect.
	Let $D: \cat I \to \EqGrph$ be a diagram, and let $((c_i)_{i\in \cat I}, \eqgraph{C})$ be the colimit of $Q \circ D$, where $\eqgraph{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
	Let now $T: \EqGrph \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.
	Let then $((b_i)_{i\in \cat I}, B)$ be the colimit of $T \circ D$.
	Consider the following situation.
	\[\begin{tikzcd}[row sep = 24, column sep = 24]
		& B & \\
		B_i \ar[ur, "{b_i}"] \ar[rr, "h_V"] \ar[d, "{q_i}"] & & B_j \ar[ul, "{b_j}"swap] \ar[d, "{q_j}" swap] \\
		C_i \ar[dr, "{c_C^i}" swap] \ar[rr, "{h_C}"swap] & & C_j \ar[dl, "{c_C^j}"] \\
		& C &
	\end{tikzcd}\]

	Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $T \circ D$, there exists a unique $q: B \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
	Consider now the functor $W: \EqGrph \to \Set$ mapping each $(X, Y, Z, x, y, z)$ onto $X$, and each morphism on its first component. By \Cref{prop:eqgrph_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, A)$ is the colimit of $W \circ D$.
	Notice that $((b_i \circ s_i)_{i \in \cat{I}}, B)$ and $((b_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one. It remains now to show that $(A, B, C, s, t, q)$, together with $(c_E^i, b_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
\end{proof}

}
